Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-07-02 main_revision.tex
Updates from Overleaf

Low values of \emph{stem\_leaf} ratio caused lower responses to fertilization for GPP and LAI at Caxiuan\~a and Harvard Forest (Figures \ref{GPP CO2 and N respones 2001} and \ref{LAI CO2 and N respones 2001}). Initial LAI was larger in these cases, explaining the decrease in fertilization response as above (lower increases in GPP for a unit change in LAI).  At Niwot Ridge, low values of \emph{stem\_leaf} were associated with very high LAI and high water limitation (Figure \ref{btran state}), and CO$_{2}$ fertilization thus had a large impact on GPP and NPP (as for \emph{slatop}), but the high NPP has no impact on LAI (SI Figure 3), reflecting the still-high N limitation.  Correspondingly, adding Nitrogen in the low \emph{stem\_leaf} runs increases LAI substantially, but only has a very limited impact on GPP and NPP, given water limitations.

>>>>

Low \emph{stem\_leaf} ratio caused lower responses to N fertilization CAX, NWR and HVF for GPP and LAI at  (Figures \ref{GPP_CN} and \ref{LAI_CN}), again mirroring the GPP-LAI non-linearity issue.  At NWR,  N limitation restricted CO$_{2}$ responses in general, but

 Correspondingly, adding Nitrogen in the low \emph{stem\_leaf} runs increases LAI substantially, but only has a very limited impact on GPP and NPP, given water limitations.
